Statistical Mechanics Informed Neural Networks for Solar Wind modeling

### 2024-12-14 paper/main.tex
default

@@

\begin{align*}
    \frac{\partial f_\alpha}{\partial t} + f_v \cdot \nabla_{\mathbf{r}} f_\alpha &+ \frac{q_\alpha ( f_E + f_v \times f_B)}{m_\alpha} \cdot \nabla_{\mathbf{v}} f_\alpha = 0 \text{ (Vlasov)}\\
\frac{d}{dt} \int &f_\alpha \log f_\alpha d^3r d^3(f_v) = 0 \text{ (Liouville)}\\
\nabla \cdot f_E &= 0 \text{ (Quasineutrality)}\\
\nabla \cdot f_B &= 0 \\
\nabla \times f_E &= - \frac{\partial f_B}{\partial t} \\
\end{align*}

@@

>>>>

\subsection{Conservation of energy}
Another important property can be provided by conservation of energy in solar wind. In this case, we want to account for the bulk motion of the particles; the interaction energy, this is the work of the fields; and the conservation of the pointing vector $S$ describing the energy transport throughout space and time.

\begin{align*}
    \frac{\partial}{\partial t} \left( \frac{1}{2} m_\alpha f_v^2 + m_\alpha q_\alpha f_E \cdot f_v\right) + \nabla \cdot \textbf{S} = 0
\end{align*}

@@

\begin{align*}
    \frac{\partial f_\alpha}{\partial t} + f_v \cdot \nabla_{\mathbf{r}} f_\alpha &+ \frac{q_\alpha ( f_E + f_v \times f_B)}{m_\alpha} \cdot \nabla_{\mathbf{v}} f_\alpha = 0 \text{ (Vlasov)}\\
\frac{d}{dt} \int &f_\alpha \log f_\alpha d^3r d^3(f_v) = 0 \text{ (Liouville)}\\
\nabla \cdot f_E &= 0 \text{ (Quasineutrality)}\\
\nabla \cdot f_B &= 0 \\
\nabla \times f_E &= - \frac{\partial f_B}{\partial t} \\
\frac{\partial}{\partial t} \left( \frac{1}{2} m_\alpha f_v^2 + m_\alpha q_\alpha f_E \cdot f_v \right) &+ \nabla \cdot \textbf{S} = 0 \text{ (Conservation)} \\
\end{align*}

@@

\section{Appendix}
